---
title: "Exploration"
author: "COMBINE Australia"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: yes
    theme: yeti
    toc: yes
    toc_float: yes
    df_print: paged
---

Code version: `r system("git log -1 --format=oneline | cut -d' ' -f1", intern = TRUE)`

```{r knitr, include = FALSE}
DOCNAME = "exploration"
knitr::opts_chunk$set(autodep        = TRUE,
                      cache          = FALSE,
                      cache.path     = paste0("cache/", DOCNAME, "/"),
                      cache.comments = TRUE,
                      echo           = FALSE,
                      error          = FALSE,
                      fig.align      = "center",
                      fig.path       = paste0("figures/", DOCNAME, "/"),
                      fig.width      = 10,
                      fig.height     = 8,
                      message        = FALSE,
                      warning        = FALSE)
```

```{r libaries, cache = FALSE}
library("lubridate")
library("here")
library("tidyverse")
```

```{r source, cache = FALSE}

```

Introduction
============

In this document we are going to read in the survey responses and make some
simple plots of each question. The goal is to see what kinds of responses we
have and what kinds of filtering or quality control we might need to do.

```{r load}
date_fmt <- "%d/%m/%Y %H:%M:%S"

col_types <- cols(
    Timestamp                                         = col_datetime(
                                                            format = date_fmt
                                                        ),
    Gender                                            = col_character(),
    Age                                               = col_integer(),
    `Indigenous status`                               = col_character(),
    Location                                          = col_character(),
    `Course level`                                    = col_character(),
    `Course year`                                     = col_character(),
    Residency                                         = col_character(),
    `Time commitment`                                 = col_character(),
    `Academic background`                             = col_character(),
    `Competencies [Genetics]`                         = col_integer(),
    `Competencies [Biochemistry]`                     = col_integer(),
    `Competencies [Probability]`                      = col_integer(),
    `Competencies [Statistical testing]`              = col_integer(),
    `Competencies [Linear algebra]`                   = col_integer(),
    `Competencies [Computational algorithms]`         = col_integer(),
    `Competencies [Programming]`                      = col_integer(),
    `Competencies [Software development]`             = col_integer(),
    Finances                                          = col_character(),
    `Coursework component?`                           = col_character(),
    Classes                                           = col_double(),
    `Coursework time`                                 = col_double(),
    Assignments                                       = col_integer(),
    Exams                                             = col_integer(),
    `Computational classes`                           = col_integer(),
    `Statistical classes`                             = col_integer(),
    `Biological classes`                              = col_integer(),
    Cohort                                            = col_character(),
    Support                                           = col_character(),
    `Coursework details`                              = col_character(),
    `Research component?`                             = col_character(),
    `Research percentage`                             = col_integer(),
    `Research time`                                   = col_integer(),
    `Research focus`                                  = col_character(),
    Institute                                         = col_character(),
    Computational                                     = col_integer(),
    `Experimental technologies and platforms`         = col_character(),
    `Programming languages`                           = col_character(),
    Collaboration                                     = col_character(),
    `Research group`                                  = col_character(),
    `Other students`                                  = col_character(),
    `Research details`                                = col_character(),
    `Number of supervisors`                           = col_integer(),
    `Primary supervisor precentage`                   = col_double(),
    `Primary supervisor gender`                       = col_character(),
    `Secondary supervisor gender`                     = col_character(),
    `Formal meetings`                                 = col_character(),
    `Informal meetings`                               = col_character(),
    `Supervisor qualities [Communication]`            = col_integer(),
    `Supervisor qualities [Inclusiveness]`            = col_integer(),
    `Supervisor qualities [Empathy]`                  = col_integer(),
    `Supervisor qualities [Subject matter expertise]` = col_integer(),
    `Supervisor qualities [Availability]`             = col_integer(),
    `Supervisor qualities [Interest in project]`      = col_integer(),
    `External activities`                             = col_character(),
    `Access to facilities`                            = col_character(),
    `Access to financial support`                     = col_character(),
    `Other support`                                   = col_character(),
    `More about your supervisor relationship`         = col_character(),
    `Familiarity with COMBINE`                        = col_character(),
    `Familiarity with the ABACBS`                     = col_character(),
    `ABACBS Membership`                               = col_character(),
    `Future COMBINE events`                           = col_character(),
    `What can we do for you?`                         = col_character()
)

responses <- read_csv(here("data", "responses_raw.csv"), col_types = col_types)
glimpse(responses)
```

General
=======

Date
----

```{r date}
responses %>%
    mutate(Date = as_date(Timestamp)) %>%
    ggplot(aes(x = Date)) +
    geom_bar()
```

Gender
------

```{r gender}
ggplot(responses, aes(x = Gender)) +
    geom_bar()
```

Age
---

```{r age}
ggplot(responses, aes(x = 1, y = Age)) +
    geom_boxplot()
```

Indigenous status
-----------------

```{r indigenous-status}
ggplot(responses, aes(x = `Indigenous status`)) +
    geom_bar()
```

Location
--------

```{r location}
ggplot(responses, aes(x = Location)) +
    geom_bar()
```

Course level
------------

```{r course-level}
ggplot(responses, aes(x = `Course level`)) +
    geom_bar()
```

Course year
-----------

```{r course-year}
ggplot(responses, aes(x = `Course year`)) +
    geom_bar()
```

Residency
---------

```{r residency}
ggplot(responses, aes(x = Residency)) +
    geom_bar()
```

Time commitment
---------------

```{r time-commitment}
ggplot(responses, aes(x = `Time commitment`)) +
    geom_bar()
```

Academic background
-------------------

```{r academic-background}
ggplot(responses, aes(x = `Academic background`)) +
    geom_bar() +
    coord_flip()
```

Competencies
------------

```{r competencies}
responses %>%
    select(starts_with("Competencies")) %>%
    gather(key = "Competency", value = "Rating") %>%
    mutate(Competency = str_remove(Competency, "Competencies \\["),
           Competency = str_remove(Competency, "\\]")) %>%
    ggplot(aes(x = Competency, y = Rating)) +
    geom_boxplot() +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

Finances
--------

```{r finances}
ggplot(responses, aes(x = Finances)) +
    geom_bar() +
    coord_flip()
```

Coursework
==========

```{r coursework}
ggplot(responses, aes(x = `Coursework component?`)) +
    geom_bar()

coursework <- responses %>% filter(`Coursework component?` == "Yes")
```

Classes
-------

```{r classes}
ggplot(coursework, aes(x = Classes)) +
    geom_bar()
```

Coursework time
---------------

```{r coursework-time}
ggplot(coursework, aes(x = 1, y = `Coursework time`)) +
    geom_boxplot()
```

Assignments
-----------

```{r assignments}
ggplot(coursework, aes(x = Assignments)) +
    geom_bar()
```

Class types
-----------

```{r types}
plot_data <- coursework %>%
    select(ends_with("classes"), -Classes) %>%
    gather(key = "Type", value = "Number") %>%
    mutate(Type = str_remove(Type, " classes"))

ggplot(plot_data, aes(x = Type, y = Number)) +
    geom_boxplot()

ggplot(plot_data, aes(x = Number)) +
    geom_bar() +
    facet_wrap(~ Type)
```

Cohort
------

```{r cohort}
ggplot(coursework, aes(x = Cohort)) +
    geom_bar()
```

Support
-------

```{r support}
ggplot(coursework, aes(x = Support)) +
    geom_bar()
```

Coursework details
------------------

```{r coursework-details}
coursework %>%
    filter(!is.na(`Coursework details`)) %>%
    pull(`Coursework details`)
```

Research
========

```{r research}
ggplot(responses, aes(x = `Research component?`)) +
    geom_bar()

research <- responses %>% filter(`Research component?` == "Yes")
```

Research percentage
-------------------

```{r research-percentage}
ggplot(research, aes(x = `Research percentage`)) +
    geom_bar()
```

Research time
-------------

```{r research-time}
ggplot(research, aes(x = `Research time`)) +
    geom_bar()
```

Research focus
--------------

```{r research-focus}
ggplot(research, aes(x = `Research focus`)) +
    geom_bar() +
    coord_flip()

unique(research$`Research focus`)
```

Institute
---------

```{r institute}
ggplot(research, aes(x = Institute)) +
    geom_bar()
```

Computational
-------------

```{r computational}
ggplot(research, aes(x = Computational)) +
    geom_bar()
```

Technologies and platforms
--------------------------

```{r technologies-platforms}
ggplot(research, aes(x = `Experimental technologies and platforms`)) +
    geom_bar() +
    coord_flip()

unique(research$`Experimental technologies and platforms`)
```

Programming languages
---------------------

```{r programming-languages}
ggplot(research, aes(x = `Programming languages`)) +
    geom_bar() +
    coord_flip()
```

Collaboration
-------------

```{r collaboration}
ggplot(research, aes(x = `Collaboration`)) +
    geom_bar() +
    coord_flip()
```

Research group
--------------

```{r research-group}
ggplot(research, aes(x = `Research group`)) +
    geom_bar()
```

Other students
--------------

```{r other-students}
ggplot(research, aes(x = `Other students`)) +
    geom_bar()
```

Research details
----------------

```{r research-details}
research %>%
    filter(!is.na(`Research details`)) %>%
    pull(`Research details`)
```

Supervisors
===========

Number of supervisors
---------------------

```{r number-supervisors}
ggplot(research, aes(x = `Number of supervisors`)) +
    geom_bar()
```

Primary percentage
------------------

```{r primary-percentage}
ggplot(research, aes(x = `Primary supervisor precentage`)) +
    geom_bar()
```

Primary gender
--------------

```{r primary-gender}
ggplot(research, aes(x = `Primary supervisor gender`)) +
    geom_bar() +
    coord_flip()
```

Secondary gender
----------------

```{r secondary-gender}
ggplot(research, aes(x = `Secondary supervisor gender`)) +
    geom_bar() +
    coord_flip()
```

Formal meetings
---------------

```{r formal-meetings}
ggplot(research, aes(x = `Formal meetings`)) +
    geom_bar()
```

Informal meetings
-----------------

```{r informal-meetings}
ggplot(research, aes(x = `Informal meetings`)) +
    geom_bar()
```

Supervisor qualities
--------------------

```{r supervisor-qualities}
research %>%
    select(starts_with("Supervisor qualities")) %>%
    gather(key = "Quality", value = "Rating") %>%
    mutate(Quality = str_remove(Quality, "Supervisor qualities \\["),
           Quality = str_remove(Quality, "\\]")) %>%
    ggplot(aes(x = Quality, y = Rating)) + 
    geom_boxplot()
```

External activities
-------------------

```{r external-activites}
ggplot(research, aes(x = `External activities`)) +
    geom_bar() +
    coord_flip()
```

Access to facilities
--------------------

```{r facilities}
ggplot(research, aes(x = `Access to facilities`)) +
    geom_bar() +
    coord_flip()
```

Access to financial support
---------------------------

```{r financial-support}
ggplot(research, aes(x = `Access to financial support`)) +
    geom_bar() +
    coord_flip()
```

Other support
-------------

```{r other-support}
ggplot(research, aes(x = `Other support`)) +
    geom_bar() +
    coord_flip()

unique(research$`Other support`)
```

Supervisor details
------------------

```{r supervisor-details}
research %>%
    filter(!is.na(`More about your supervisor relationship`)) %>%
    pull(`More about your supervisor relationship`)
```

Involvement
===========

COMBINE
-------

```{r combine}
ggplot(responses, aes(x = `Familiarity with COMBINE`)) +
    geom_bar() +
    coord_flip()

unique(responses$`Familiarity with COMBINE`)
```

ABACBS
------

```{r abacbs}
ggplot(responses, aes(x = `Familiarity with the ABACBS`)) +
    geom_bar() +
    coord_flip()

unique(responses$`Familiarity with the ABACBS`)
```

ABACBS membership
-----------------

```{r abacbs-membership}
ggplot(responses, aes(x = `ABACBS Membership`)) +
    geom_bar() +
    coord_flip()

unique(responses$`ABACBS Membership`)
```

Future COMBINE events
---------------------

```{r future-combine}
ggplot(responses, aes(x = `Future COMBINE events`)) +
    geom_bar() +
    coord_flip()

unique(responses$`Future COMBINE events`)
```

What can we do for you?
-----------------------

```{r combine-do}
responses %>%
    filter(!is.na(`What can we do for you?`)) %>%
    pull(`What can we do for you?`)
```

Session info
============

```{r session-info, cache = FALSE}
devtools::session_info()
```

```{r cleanup-docs, cache = FALSE}
doc.files <- c(list.files(pattern = "pdf"),
               list.files(pattern = "html"),
               list.files(pattern = "docx"))

for (file in doc.files) {
    file.rename(file, file.path("../docs", file))
}
```
